\subsection{Appropriate Data for FL}

FL, especially cross-device FL, specializes in massive numbers of heterogeneous devices with diverse non-IID data.
For FL, one can use conventional datasets, such as MNIST or CIFAR10.
However, such homogeneous and IID data is not representative of data found on real devices.
Many works in the field of FL specialize and compare how well they perform on non-IID data (\ref{subsection:fl_research}).
For this reason, various datasets and benchmarks have been created explicitly for FL.
One recurring prominent FL benchmarking tool is LEAF \cite{paper:leaf_fl_benchmark}.
It does not solely specialize in FL but in more general federated settings.
It includes several implementations and datasets.
As mentioned in Table \ref{table:fl_research_table_2}, we had little success working with this benchmark.
This finding is noteworthy because LEAF seems to be the primary and sole source for the FEMNIST dataset, which many FL papers mention and use for evaluation.

FEMNIST seems to be one of the most popular dedicated FL benchmarking datasets.
It is a federated version of the Extended MNIST (EMNIST \cite{emnist_dataset}) dataset.
FEMNIST splits the EMNIST dataset into multiple classes or data partitions based on individual (digit/symbol) writers.
Extended projects exist that wrap the access to FEMNIST via the high-speed HDF5 binary data format \cite{hdf5_femnist}.
The FEMNIST dataset is a prominent example of many dedicated FL datasets and benchmarks.
A detailed listing and comparison of other similar resources is available in \cite{thesis:tum_fl_framework_comparison}.

FLOps requires a convenient way of accessing suitable data for development and testing purposes.
Our experience trying out LEAF taught us that using these dedicated datasets can be challenging and error-prone.
Instead of figuring out how to unify these different dedicated FL datasets and benchmarks, we use Flower Datasets \cite{flower:datasets}.
We already discussed Flower Datasets briefly in \ref{subsection:flower}.
The vital thing to know about this young project is that it uses and splits up Hugging Face datasets into non-IID data fragments.
It enables users to turn conventional ML datasets into FL-optimized ones.
Users can configure this approach freely.