\subsection{Flower} \label{subsection:flower}

Flower \cite{paper:flower} is a research-backed open-source FL framework.
One major target in Flower's paper was to narrow the gap between research and production.
It allows researchers to run high-performance FL simulations and rapidly transition to tangible production environments using the same tool.
Another focal point of its paper was scale and parallelization.

Flower is a sophisticated, feature-rich FL framework.
Flower's first release (0.10.0) was published in November 2020, and its first major release (1.0.0) was published in 2022 \cite{fl_framework:flower}.
Flower supports all major operating systems, containerization, and ML libraries.
It aims to be easily customizable and extendable via a programming language and ML framework agnostic design.
Flower strives to offer all popular FL features, such as support for different data types and distributions.
Further features include pre-implemented popular FL algorithms and vertical and horizontal data splitting support.
Flower supports traditional ML tasks, like regression or clustering, DNNs, LLMs, and security mechanisms, such as secure aggregation.
It enables the use of FL via CPUs or GPUs.
The default communication protocol is gRPC, which can be replaced.
Flower supports various FL variants, including PFL, edge computing, cross-silo, and cross-device.
It handles and implements core FL components but does not handle many other aspects, like deployment, orchestration, dependency management, or containerization.
Flower offers a mature set of FL simulation techniques.

Users can easily change and add functionality to the framework by interacting with flexible abstractions and interfaces.
The heart of Flower is its strategy concept.
The aggregator uses this strategy to manage the FL processes.
A strategy contains all necessary configurations, such as the FL algorithm and the minimum number of learners required for training or evaluation.
Users can pick from more than 30 existing strategies \cite{flower:strategies} or extend from basic strategies and develop their own behavior.
It does not have native out-of-the-box support for model pruning, advanced security/privacy techniques, CFL, HFL, MLOps, or orchestration.
Due to Flowers' flexible design, users can implement their custom features and strategies based on the available basic Flower components.

It is straightforward to set up Flower and start working with it.
Flower is directly available via Python's default package manager pip.
One has to define the server/aggregator, strategy, and clients/learners.
Users can implement the simplest case with a few dozen lines of Python code.
The crucial part is to configure the strategy and clients properly.
One needs to create a client class that extends from a Flower client and implement four essential methods that the framework will call during training.
These methods include a getter and setter for the model parameters and one method each for training/fitting and evaluating the model.
In conclusion, Flower provides a rapid and easy onboarding experience.

Flower has a modern, user-friendly, growing ecosystem.
A dedicated sub-project called Flower Datasets \cite{flower:datasets} is part of this ecosystem.
This project is still in its infancy (v0.3.0).
It allows users to pull HuggingFace \cite{hugging_face_homepage} datasets easily and split them into FL-optimized data fragments.
Users can configure how to split this data up.
Flower Datasets can turn standard non-federated homogeneous/IID datasets into challenging, federated, non-IID data, which is ideal for FL research and development.
This ecosystem includes a well-structured and rich homepage \cite{flower:homepage}, an extensive set of tutorials, guides, example projects \cite{flower:examples}, and documentation \cite{flower:homepage_docs, flower_docs} that ranges from beginner-friendly to advanced.
They have open monthly community events \cite{flower:monthly}, yearly summits \cite{flower:summit}, a blog \cite{flower:blog}, a discussion forum \cite{flower:forum}, a Slack space \cite{flower:slack}, and a YouTube channel \cite{flower:youtube}.