\chapter{\abstractname}

% Background 1 Sentence - FL briefly what it is and why it is increasing in popularity
Federated Learning (FL) is a significant distributed machine learning technique that enables training on sensitive private data instead of centrally collecting it and violating laws and regulations.
% Literature (without bad-dark sides) ~ 2 sentences 
The field of FL is a young and thriving domain that focuses on improving and inventing new algorithms and methods to advance performance and security.
These numerous optimizations gave way to various FL sub-categories with specific strategies and architectures.
% Problem - gap in FL literature - ignore applicability/automation - do not mention how to replicate/do FL
Only a minuscule number of FL researchers focus on the practical setup, configuration, deployment, and practical application of FL.
Most works do not mention the tools they used to execute their FL experiments, making replicating or extending their findings infeasible.
% Methods - what did we do - e.g. in this work we implemented FLOps ... (~ 1 sentence)
In this work, we implemented a novel system for performing, developing, and experimenting with FL regardless of one's individual level of expertise.
This is possible by combining state-of-the-art solutions and techniques from different domains, such as automation, DevOps, MLOps, containerization, and orchestration, and applying them to FL.
Thus, users can provide their pure ML code for automatic FL augmentation, containerization, deployment, and execution.
After training and evaluation, users can access their FL-trained models or use automatically built and deployed matching inference servers.
Users can freely configure various aspects of these steps, such as the FL type, which includes conventional and clustered hierarchical FL.
These steps can run on multiple architectures, including AMD and ARM.
% summarize findings/results - numbers/clearly - focus on impact
We evaluated and verified our solution on different device constellations with diverse configurations and found that it automatically creates properly trained final models.
% implications - further investigations needed in FLOps techniques and applications (maybe 1 sentence)
Our solution is a proof of concept and a foundational piece that can and should be enhanced further to increase the number of supported FL techniques.
This work demonstrates the benefits of utilizing the mentioned cross-domain capabilities and aims to inspire FL practitioners and researchers to investigate and use these methods to make FL more accessible and application-oriented, thus helping the entire field to prosper.