\addcontentsline{toc}{chapter}{Acknowledgments}
\thispagestyle{empty}

\vspace*{20mm}

\begin{center}
    {\usekomafont{sectioning}\usekomafont{section} Acknowledgments}
\end{center}

\vspace{10mm}


Words can only attempt to express my gratitude towards the individuals who paved the path, guided, and accompanied me on this journey through hardships and triumphs in these thunderous times.
\vspace{5mm}\newline
I thank all the people at TUM, from the prominent to those working in the background, who helped to expand my knowledge and skill set.
I thank the people from the Chair of Connected Mobility for enabling me to do and finalize my thesis.

I am incredibly grateful for the dedicated time, expertise, and supervision of Giovanni Bartolomeo and Dr. Nitinder Mohan.

I thank the Oakestra team for their continuous support and pleasant camaraderie.
Thank you, Simon Zelenski, for sharing your networking prowess with me, and thank you, Ernst Bayer, for providing the evaluation infrastructure.
\vspace{5mm}\newline
I thank my instructive work colleagues at Cartken for enduring my limited part-time capabilities so I could pursue a full-time master's degree.
\vspace{5mm}\newline
A heartful thank you to my dear friends Julian, Felix, Ksenia, Dominik, and Jack, with whom I shared laughter, who lifted my spirits, and reminded me of life beyond work.
\vspace{5mm}\newline
No words can describe or outweigh the endless love, patience, and peace of mind I owe to my parents.
\vspace{5mm}\newline
To those that we have lost \newline
My heart breaks that you are no longer with us to enjoy the fruitful years to come. \newline
I hope that you have found your peace.

\vspace{10mm}
\begin{flushright}
    \centering
    \rightskip=1.8cm\textit{``May the wind under your wings bear you where the sun sails and the moon walks.''} \\
    \vspace{.2em}
    \rightskip=.8cm---J.R.R. Tolkien
\end{flushright}
\vspace{1em}

\cleardoublepage{}
