\section{CLI}

While developing FLOps, we implemented several different pieces of code to automate tedious, repetitive manual tasks.
We decided to share and offer these custom auxiliary scripts by combining them into a single CLI tool called OAK CLI \cite{cli_code}.
We have steadily improved it over this work, which resulted in various features.
Because of the envisioned rapid changes in the future, we will not discuss concrete technical details but provide a broad overview of its capabilities.
We decided to discuss this CLI as part of this work because FLOps can be considered DevOps for FL, and DevOps also includes techniques to improve development workflows.
One way to support users and developers is to help them use the target application more conveniently, for example, via a CLI tool.
Notably, Oakestra has a custom early-stage work-in-progress GUI/Frontend dashboard application \cite{oakestra_dashboard} and a minimal CLI tool.
The OAK CLI is independent of both these components and replaced the legacy Oakestra CLI tool.

We were motivated to create this CLI to alleviate the following challenges.
FLOps does not offer a tool besides the OAK CLI to interact conveniently with its API.
External tools like Postman are necessary to do so.
Oakestra components need to be prepared and launched manually.
Interacting with its API is possible via external tools or its early-stage dashboard.
We needed to work on several devices while developing FLOps, especially its HFL features.
Each machine must be appropriately configured and set up to enable Oakestra workloads.
This setup included installing dependencies such as Docker, Golang, and other custom aliases and scripts to launch, clear, and restart Oakestra components.
In addition, developing and observing FLOps was heavily bound to the observatory features provided by Oakestra's dashboard application.
Accessing and working with this dashboard was cumbersome even during local development on a single machine because of repetitive click-based tasks such as mandatory logins.
We automated this by creating auto-clicker scripts via Selenium.
Accessing this flaky dashboard on remote devices behind firewalls required even more manual steps, such as code modifications and multiple SSH tunnels.
We only required the dashboard to get an overview of the deployed application and services and their statuses and logs.
The OAK CLI satisfies these needs independently, bypassing our need for the dashboard while automating manual steps.
As a result, this CLI significantly accelerates the development and usage of FLOps and Oakestra.

\input{chapters/implementation_details/sections/cli/subsections/cli_requirements.tex}

\subsection{High Level CLI Details}

The CLI can create, delete, and (un)deploy applications and services.
It can present current information about available apps and services in different verbosity levels.
In addition, it allows to inspect latest service logs.
Users can use the CLI to manage FLOps components, including its manager, database, projects, and tracking server.
The CLI automates tedious manual tasks such as clearing local images or rebuilding orchestrator components.
It can install fundamental dependencies such as Docker and Golang.
The CLI has a customizable config file that allows users to specify their intended use case and filter out unwanted commands.
It also features experimental commands to run automatic evaluations.
Detailed descriptions of the CLI commands and options with screenshots are available in the appendix \ref{appendix:cli}.